\documentclass{my_cv}

\begin{document}
\begin{multicols}{2}[
    \titletext{Gabriel}%
        {Ligoski}%  
        {Software Developer}%
        {\href{mailto:gabriel.ligoski@gmail.com}{gabriel.ligoski@gmail.com}}%
        {+55 61 99611-1781}%
        {\href{https://github.com/gabrielligoski}{gabrielligoski} }%
        {\href{https://www.linkedin.com/in/gabriel-ligoski/}{gabriel-ligoski} }%
]
\end{multicols}
\vspace{15mm}
\section{\faFileText}{SUMMARY}
I'm an undergraduate student in Bachelor of Computer Science (BCompSc) at the University of Brasília (UnB). I have passion for new technologies and I´m always searching for new challenges and getting new knowledge.

\vspace{5mm}

\begin{multicols}{2}
\section{\faPencil}{WORK}
    
\work{FullStack Intern / May 2021 - Today}%
    {Vobys}%
    {I worked as a fullstack developer using React as frontend \& Java Spring as backend.
    Developing a management platform.}%
    {Github, Java, Spring, Docker, React, Javascript, Jhipster}
    
\section{\faList}{SKILLS}

\textbf{Languages:} Java, Python, C, C\#, JavaScript, HTML, CSS, Assembly

\noindent\textbf{Tools:} React, Tailwind, Material-ui, Spring, Heroku, Tensorflow, Selenium, MySql, Postgresql, NumPy, Pandas, Docker

\noindent\textbf{Other:} Version Control, Web, Data science and ML, Cloud computing



\section{\faGraduationCap}{EDUCATION}

\school{Bachelor of Computer Science - 4.4638/5.00 - 2019} %
{University of Brasília(UnB), Brasília. DF} %
{}

\section{\faPaintBrush}{OTHER PROJECTS}
\begin{itemize}[noitemsep]
    \item I created an app of assistance for football coaches as a freelancer, using React Native.
    \item I created a discord bot in python, using git to upload the application to cloud on heroku.
    \item I made an application using Tensorflow and web scrapping to create an AI that predicts results of E-sports matches.
    \item I created a JSP (Java Server Pages) site and database MySql data for event management with attendance list.
    \item Working as a freelancer for Vobys I migrated data from a Postgres database to
Oracle using pentaho.
    \item I uploaded some of my applications to cloud using Gcloud and Heroku, using Ubuntu and Git respectively.
\end{itemize}

\section{\faStar}{CERTIFICATION}

\begin{itemize}[noitemsep]
    \item Java OCAJP 1Z0-808 - Oracle Certified Associate Java Programmer SE 8 Programmer I
\end{itemize}

\section{\faSoccerBallO}{ACTIVITIES / INTERESTS}

Proactive about learning diverse things and happy to discuss those. Favorite physical activities would be volleyball and krav maga.


\end{multicols}
\end{document}
